\section{State of the Art}
\begin{frame}
    Given $a \in A$ consider the set of codewords with fixed value $a$ at coordinate $i$:

    $$ \C (i,a) = \{ x \in \C : x_i = a \}, \quad i \in [n] $$ \\~\\
    
    For $I \subseteq [n]$ let $\C_I$ be the restriction of the code $\C$ to the coordinate set $I$:
    
    $$\C_I := \{(x_i)_{ i \in I } \vert (x_1, ..., x_n) \in \C\}$$
    
        
\end{frame}

\begin{frame}
    \begin{defn}
        A code $\C$ of length $n$ has \textbf{locality r} if \\~\\
        
        $\ \forall i \in [n ]$, $\quad \exists I_i \subseteq [n] \setminus \{i\}, \quad \vert I_i \vert \leq r \quad $ s.t.         
        $$\C_{I_i} (i,a) \cap \C_{I_i} (i,a') = \emptyset, \quad a \neq a'.$$
    \end{defn}
    
	\begin{defn}
	    A code $\C$ of length $n$ is said to \textbf{have $t$ disjoint recovering sets} if \\~\\
	    
	    $\forall i \in [n]$, $\quad \exists R_i^1, ..., R_i^t \subset [n] \setminus \{i\}$ pairwise disjoint subsets
	    s.t. 
	    $$\C_{R_i^j} (i,a) \cap \C_{R_i^j} (i,a') = \emptyset, \quad a \neq a', \ \forall j \in [t]$$
	\end{defn}
\end{frame}

\begin{frame}
\begin{itemize}
\item Let $\C$ be a linear code of length $n$ and dimension $k$.

\item We say $\C$ is an $(n,k,r)$-LRC code if it has locality $r$ and has a single recovering set for each coordinate.

\item We say $\C$ is an $(n,k,r,t)$-LRC code if it has $t \geq 2$ recovering sets for each coordinate.
\end{itemize}
\end{frame}

\begin{frame}{Bounds on LRC parameters}
	Let $\C$ be an $(n,k,r)$ LRC code. Then:
    \begin{thm}[Upper bound on the rate]
        The rate of $\C$ satisfies
        $$ \frac{k}{n} \leq \frac{r}{r+1} $$
    \end{thm}
    
    \begin{thm}[Extension of Singleton bound]
        \label{thm:singl1}
        The minimum distance of $\C$ satisfies
            $$d \leq n - k - \left\lceil \frac{k}{r} \right\rceil + 2$$
        If equality holds, we call $\C$ an \textbf{optimal LRC code}.
    \end{thm}
\end{frame}

\begin{frame}{Bounds on LRC parameters}
Let $\C$ be an $(n,k,r,t)$ LRC code. Then:
    \begin{thm}[Extension of Singleton bound for $t\geq 2$]
        \label{thm:singl2}
        The minimum distance of $\C$ is bounded as follows
        $$d \leq n - k + 2 - \left\lceil \frac{t(k-1)+1}{t(r-1)+1} \right\rceil $$
    \end{thm}
    
    In particular, for $t=1$, the bound matches the one in Theorem \ref{thm:singl1}.
    
\end{frame}



\begin{frame}{Bounds on LRC parameters}
    Let $\C$ be an $(n,k,r,t)$ LRC code. Then:
    \begin{thm}
        \label{thm:max_rate_t}
        The rate of $\C$ satisfies
        $$ \frac{k}{n} \leq \frac{1}{\prod_{j=1}^{t} (1 + \frac{1}{jr} )} $$
    \end{thm}
    
    \begin{thm}
        \label{thm:min_dist_t}
        The minimum distance of $C$ is bounded above as follows
        $$ d \leq n - \sum_{i=0}^{t} \left\lfloor \frac{k-1}{r^i} \right\rfloor $$
    \end{thm}
\end{frame}   

\input{parts/LRC_construction}

\input{parts/LRC_example}

\begin{frame}{Algebraic Geometric Codes}
\begin{itemize}
\item $X,Y$ smooth projective absolutely irreducible curves.

\item $g: X \rightarrow Y$ rational separable map of degree $r+1$

\item $g*: K(Y) \rightarrow K(X)$ associated function field mapping.

\item $g*$ defines a field embedding $K(Y) \hookrightarrow K(X)$ when identifying $K(Y)$ with its image.

\item Primitive element theorem: $\exists x \in K(X)$ s.t. $K(X) = K(Y)(x)$
and $x^{r+1} + b_r x^r + ... + b_0 = 0$ for some $b_i \in K(Y)$.

\item Denote $deg(x) = h$

\item $S = \{ P_1, ..., P_s \} \subset Y(K)$

\item Let $D \geq 0$ a divisior, deg$(D) = \ell \geq 1$, with supp$(D) \cap S = \emptyset$
\end{itemize}
\end{frame}

\begin{frame}
\begin{itemize}
\item Assumptions:
\begin{itemize}
\item $A := g^{-1}(S) = \{P_{ij}, i=0,...,r, \ j=1,...,s\} \subseteq X(K)$

\item $g(P_{ij}) = P_j$ for all $i,j$

\item $b_i \in L(n_i D), \ i=0,...,r$ for some $n_i \in \mathbb{N}$
\end{itemize}

\item Let $\{ f_1, ..., f_m \}$ basis of $L(D)$.

\item Functions $f_i$ contained in $K(Y) \Rightarrow$ constant on the fibers of $g$.

\item Riemann-Roch theorem: $m \geq \ell - g_Y +1$, ($g_Y$ genus of $Y$)

\item Consider the subspace $V:=\{f_j x^i, i=0,...,r-1, \ j=1,...,m\}$

\begin{tabular}{rccl}
$e := ev_A:$ & $V$ & $\rightarrow$ & $K^{(r+1)s}$ \\
            & $F$ & $\mapsto$ & $(F(P_{ij}), i=0,...,r, \ j=1,...,s)$
\end{tabular}

\end{itemize}
\end{frame}

\begin{frame}
    Let $\C(D,g)$ be the image of the mapping: $e(V) \subseteq \FF_q^{(r+1)s}$.
    \begin{theorem}
        The subspace $\C(D,g)$ forms an $(n,k,r)$ linear LRC code with the parameters:
        $$        
        \left.                
        \begin{matrix}
        n = (r+1)s \\
        k = rm \geq r(\ell - g_Y + 1) \\
        d \geq n - \ell ( r+1) - (r-1)h
        \end{matrix}                
        \right\rbrace
        $$
    \end{theorem}
    Code coordinates partitioned into $s$ subsets $A_j = \{P_{ij}, i = 0, ..., r\}$
    
    Local recovery of erased symbol $c_{ij} = F(P_{ij})$ can be performed by polynomial interpolation through the points of $A_j$.
\end{frame}

\begin{frame}
    Extending this construction to:
    \begin{itemize}
    \item Families of curves (Hermitian curves and Garcia-Stichtenoth curves)
    \item Higher-dimensional varieties
    \end{itemize}
    Authors constructed optimal LRC codes with large code lentgh. E.g. $n=q^2-1$ and $n=q^2+2$.
\end{frame}

\begin{frame}{List Decoding}
A code $\C$ of length $n$ over an alphabet $A$ of size $q$ is $(\tau, \ell)$-list decodable if:
$$\forall v \in A^n \quad \vert \{ c \in \C \vert d(v,c) \leq \tau \} \vert \leq \ell $$

Johnson showed any code of length $n$ and distance $d$ is $(\tau_J, \ell)$-list decodable, where:
\begin{itemize}
\item $\tau_J = n - \sqrt{n(n-d)}$ the Johnson radius
\item Size of list $\ell$ polynomial in $n$.
\end{itemize}
\end{frame}
\begin{frame}{List Decoding}
Holzbaur and Wachter-Zeh improved the Johnson radius for LRC codes
\begin{itemize}
\item List decode each recovering set 
\item List decode the LRC code using combinations of previously decoded recovering sets.
\end{itemize}

Complexity and list size polynomial in $n$ when number of recovering sets remain constant.

\end{frame}