\section{Work Plan}
\subsection{Open Problems}

\begin{frame}{Improvement of Bounds}
Bound appears to be far from tight.
$$ \frac{k}{n} \leq \frac{1}{\prod_{j=1}^{t} (1 + \frac{1}{jr} )} $$
Authors believe largest possible rate for $(n,k,r,t)$-LRC code is $\left(\frac{r}{r+1}\right)^t$ as long as $t$ not too large (e.g. $t\in O(\log n)$).
\end{frame}

\begin{frame}{List Decoding}

\end{frame}

\subsection{Time Plan and Methodology}
\begin{frame}{First Year}
Goal: Research of the state of the art, and stating the problems to study.
\begin{itemize}
\item Master's Degree in Advanced Mathematics and Mathematical Engineering
\item Visitor student in University of Maryland, with prof. Alexander Barg
\item Algebraic Geometry Seminar. Two sessions per week.
\begin{itemize}
\item \textit{"Algebraic Curves"}. William Fulton
\item Lecture notes on Algebraic Geometry, Andreas Gathmann
\item Lecture notes on Plane Algebraic Curves, Andreas Gathmann
\end{itemize}
\item Self-Learning: \textit{"The Probabilistic Method"}, Alon and Spencer.
\end{itemize}
\end{frame}

\begin{frame}{Second Year}
Goal: Work on the stated problems.
\begin{itemize}
\item Seminars
\begin{itemize}
\item Algebraic Geometric Codes, two sessions per week.
\begin{itemize}
\item \textit{"Algebraic Geometric Codes: basic notions"}; Vladut, Nogin and Tsfasman.
\item \textit{"Algebraic Function Fields and Codes"}, Stichtenoth.
\end{itemize}
\item Probabilistic Method, two sessions per week.
\begin{itemize}
\item \textit{"The Probabilistic Method"}, Alon and Spencer.
\end{itemize}
\end{itemize}
\item Self-Learning: \textit{"The Theory of Error-Correcting Codes"}, MacWilliams and Sloane.
\end{itemize}
\end{frame}

\begin{frame}{Third Year}
Goal: Conclude research and write thesis.
\begin{itemize}
\item Conclusion of the research
\item Writing of PhD thesis.
\end{itemize}
\end{frame}